### 2018-01-02 derivations.tex
updates

\documentclass[12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{csquotes}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage[
    backend=biber,
    style=numeric,
    citestyle=numeric,
    sorting=none
]{biblatex}
\addbibresource{derivations.bib}
% dcases
\usepackage{mathtools}
% for text right arrow
\usepackage{textcomp}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage[breaklinks=true, linkcolor=blue, citecolor=blue, colorlinks=true]{hyperref}
% load after hyperref
\usepackage[english,capitalise]{cleveref}

\newcommand{\pluseq}{\mathrel{{+}{=}}}
\newcommand{\minuseq}{\mathrel{{-}{=}}}
\newcommand{\ns}{\ensuremath{{N_{sp}}}}
\newcommand{\nr}{\ensuremath{{N_{reac}}}}
\newcommand{\conp}{CONP}
\newcommand{\conv}{CONV}
\newcommand{\dconp}{\ensuremath{,\qquad\text{for \conp}}}
\newcommand{\dconv}{\ensuremath{,\qquad\text{for \conv}}}
\newcommand{\Ru}{\ensuremath{\mathcal{R}}}

@@

\subsection{Reaction rate expressions}
The net species rate of production is defined as:
\begin{equation}
 \label{e:spec_rop}
 \dot{\omega}_{k} = \sum_{i=1}^{\nr} \nu_{k,i} q_{i}
\end{equation}
where $\nr$ is the number of reactions in the chemical kinetic model, $\nu_{k, i}$ the overall stoichiometric coefficient of species $k$ in reaction $i$ and $q_i$ the net rate-of-progress for reaction $i$:
\begin{align}
\nu_{k,i} &= \nu^{\prime\prime}_{k,i} - \nu^{\prime}_{k,i} \\
q_{i} &= R_{i} c_{i}
\end{align}
with $\nu^{\prime}_{k,i}$ and $\nu^{\prime\prime}_{k,i}$ the product and reactant stoichiometric cofficients (respectively) of species $k$ in reaction $i$.
The base rate-of-progress for the $i$th reversible reaction $R_{i}$ is given by:
\begin{align}
R_{i} &= {R_f}_{i} - {R_r}_{i} \label{e:ropnet}\\
{R_f}_{i} &= {k_f}_{i} \prod_{k=1}^{\ns} [C]_{k}^{\nu^{\prime}_{k,i}} \label{e:ropf}\\
{R_r}_{i} &= {k_r}_{i} \prod_{k=1}^{\ns} [C]_{k}^{\nu^{\prime\prime}_{k,i}} \label{e:ropr}
\end{align}
where ${k_f}_{i}$ and ${k_r}_{i}$ are the forward and reverse reaction coefficients (respectively) for the $i$th reaction, and the third-body\slash pressure modification $c_{i}$ is given by:
\begin{equation}
\label{e:rxn_pressure}
c_i = \begin{dcases}
  1 &\text{for elementary reactions,} \\
  [X]_i &\text{for third-body enhanced reactions,} \\
  \frac{P_{r,i}}{1 + P_{r,i}} F_i &\text{for unimolecular/recombination falloff reactions, and} \\
  \frac{1}{1 + P_{r,i}} F_i &\text{for chemically-activated bimolecular reactions,}
  \end{dcases}
\end{equation}
where for the $i$th reaction $[X]_i$ is the third-body concentration, $P_{r,i}$ is the reduced pressure, and $F_i$ is the falloff blending factor.
These terms are defined in the following sections.

@@

\subsection{Falloff reactions}
Unlike elementary and third-body reactions, falloff reactions exhibit a pressure dependence described as a blending of rates at low- and high-pressure limits; thus, the rate coefficients depend on a mixture of low-pressure- ($k_{0, i}$) and high-pressure-limit ($k_{\infty,i}$) coefficients, each with corresponding Arrhenius parameters and expressed using Eq.~\cref{e:arrhenius}.
The ratio of the coefficients $k_{0, i}$ and $k_{\infty, i}$, combined with the third-body concentration (based on either the mixture as a whole including any efficiencies $\alpha_{k,i}$, or a specific species), define a reduced pressure $P_{r,i}$ given by
\begin{equation}
 P_{r, i}=\frac{[X]_{i} k_{0, i}}{k_{\infty, i}}
\end{equation}
where $[X]_{i}$ is the appropriate third-body concentration as described in~\cref{s:thdbody}

@@

\subsection{Species rate of production derivatives}
First, we evaluate the derivatives of the net species rate of production equation~\cref{e:spec_rop}, with respect to temperature:
\begin{equation}
 \label{e:dwdot_dT}
 \frac{\partial \dot{\omega} }{\partial T }_{k} = \sum_{i=1}^{\nr} \left(\nu_{k,i} R_{i} \frac{\partial c }{\partial T }_{i} + \nu_{k,i} \frac{\partial R }{\partial T }_{i} c_{i}\right) \;,
\end{equation}
other species:
\begin{equation}
 \label{e:dwdot_dnj}
 \frac{\partial \dot{\omega} }{\partial n[j] }_{k} = \sum_{i=1}^{\nr} \left(\nu_{k,i} R_{i} \frac{\partial c }{\partial n[j] }_{i} + \nu_{k,i} \frac{\partial R }{\partial n[j] }_{i} c_{i}\right)
\end{equation}
and the state parameter:
\begin{subequations}
 \label{e:dwdot_de}
 \begin{align}
  \frac{\partial \dot{\omega} }{\partial V }_{k} &= \sum_{i=1}^{\nr} \left(\nu_{k,i} R_{i} \frac{\partial c }{\partial V }_{i} + \nu_{k,i} \frac{\partial R }{\partial V }_{i} c_{i}\right)\dconp,\\
  \frac{\partial \dot{\omega} }{\partial P }_{k} &= \sum_{i=1}^{\nr} \left(\nu_{k,i} R_{i} \frac{\partial c }{\partial P }_{i} + \nu_{k,i} \frac{\partial R }{\partial P }_{i} c_{i}\right)\dconv
 \end{align}
\end{subequations}

@@

Finally, combining~\cref{e:dropf_dt,e:dropr_dt} gives the total temperature derivative of the net rate of progress:
\begin{align}
 \label{e:drop_dt}
 \frac{\partial R }{\partial T }_{i} =& \frac{{R_f}_{i}}{T} \left(\beta_{i} + \frac{{E_{a}}_{i}}{T \Ru}\right) - \left(- \sum_{k=1}^{\ns} \nu_{k,i} \frac{\text{d} B }{\text{d} T }_{k} + \frac{1}{T} \left(\beta_{i} + \frac{{E_{a}}_{i}}{T \Ru}\right)\right) {R_r}_{i} \nonumber \\
				      &\qquad + \frac{[C] S^{\prime\prime}_{\ns}}{T} {k_r}_{i} - \frac{[C] S^{\prime}_{\ns}}{T} {k_f}_{i}
\end{align}
\subsubsection{Molar derivative}
\label{s:rop_molar}
The derivative of the forward rate of progress with respect to the amount of moles of a species $j$ is:
\begin{equation}
 \frac{d}{d n_{k}} {R_f} = \left(\frac{\partial}{\partial n_{j}} \prod_{k=1}^{\ns} [C]_{k}^{\nu^{\prime}_{k,i}}\right) {k_f}_{i} \;.
\end{equation}
The derivative of a species concentration with respect to moles of a species $j$ is given as:
\begin{equation}
 \frac{\partial [C_k]}{\partial n_j} =
 \begin{dcases}
 \frac{\delta_{j k}}{V} & k \ne \ns \\
 -\frac{1}{V} & k = \ns
 \end{dcases}
\end{equation}
Or put succinctly:
\begin{equation}
\label{e:dck_dnj}
\frac{\partial [C_k]}{\partial n_j} = \frac{\delta_{j k} - \delta_{\ns k}}{V} \;.
\end{equation}
Using~\cref{e:dck_dnj} the molar derivative of the forward rate of progress is found as:
\begin{equation}
 \frac{\partial {R_f} }{\partial n[j] }_{i} = {k_f}_{i} \sum_{k=1}^{\ns} \left(- \frac{\delta_{\ns k}}{V} + \frac{\delta_{j k}}{V}\right) \nu^{\prime}_{k,i} [C]_{k}^{\nu^{\prime}_{k,i} - 1} \prod_{\substack{1 \leq l \leq k - 1\\k + 1 \leq l \leq \ns}} [C]_{l}^{\nu^{\prime}_{l,i}}
\end{equation}
with the same temporary variables $S^{\prime}_{j}$ and $S^{\prime}_{\ns}$ as defined previously, this can be simplified to:
\begin{equation}
 \label{e:dropf_dnj}
 \frac{\partial {R_f} }{\partial n[j] }_{i} = \frac{{k_f}_{i}}{V} \left(- S^{\prime}_{\ns} + S^{\prime}_{j}\right)
\end{equation}
and by the same process, the reverse rate of progress derivative is found to be:
\begin{equation}
 \label{e:dropr_dnj}
 \frac{\partial {R_r} }{\partial n[j] }_{i} = \frac{{k_r}_{i}}{V} \left(- S^{\prime\prime}_{\ns} + S^{\prime\prime}_{j}\right)
\end{equation}
and the net rate of progress molar derivative:
\begin{equation}
 \frac{\partial R }{\partial n[j] }_{i} = - \frac{{k_r}_{i}}{V} \left(- S^{\prime\prime}_{\ns} + S^{\prime\prime}_{j}\right) + \frac{{k_f}_{i}}{V} \left(- S^{\prime}_{\ns} + S^{\prime}_{j}\right)
\end{equation}

@@

Following the outline of~\cref{s:rop_molar}, the forward rate of progress derivatives are:
\begin{subequations}
 \begin{align}
  \frac{\partial {R_f} }{\partial V }_{i} &= \frac{[C] S^{\prime}_{\ns}}{V} {k_f}_{i} - \frac{{R_f}_{i}}{V} \sum_{k=1}^{\ns} \nu^{\prime}_{k,i}&\dconp\\
  \frac{\partial {R_f} }{\partial P }_{i} &= \frac{S^{\prime}_{\ns} {k_f}_{i}}{T \Ru}&\dconv
 \end{align}
\end{subequations}
and similarly, the reverse rate of progress derivatives:
\begin{subequations}
 \begin{align}
  \frac{\partial {R_r} }{\partial V }_{i} &= \frac{[C] S^{\prime\prime}_{\ns}}{V} {k_r}_{i} - \frac{{R_r}_{i}}{V} \sum_{k=1}^{\ns} \nu^{\prime\prime}_{k,i}&\dconp\\
  \frac{\partial {R_r} }{\partial P }_{i} &= \frac{S^{\prime\prime}_{\ns} {k_r}_{i}}{T \Ru}&\dconv
 \end{align}
\end{subequations}
giving finally:
\begin{subequations}
 \label{e:dropi_de}
 % linebreak and parenthesis sizing:
 % https://tex.stackexchange.com/questions/49890/linebreak-between-left-and-right/49895
 \begin{align}
  \frac{\partial {R} }{\partial V }_{i} &= \frac{1}{V}\left(\vphantom{{R_r}_{i} \sum_{k=1}^{\ns} \nu^{\prime\prime}_{k,i}} [C]\left(S^{\prime}_{\ns} {k_f}_{i} - S^{\prime\prime}_{\ns} {k_r}_{i}\right) + \right.& \nonumber\\
  &\left. \quad\left({R_r}_{i} \sum_{k=1}^{\ns} \nu^{\prime\prime}_{k,i} - {R_f}_{i} \sum_{k=1}^{\ns} \nu^{\prime}_{k,i}\right) \right)&\dconp\\
  \frac{\partial {R} }{\partial P }_{i} &= \frac{1}{T \Ru} \left(S^{\prime}_{\ns} {k_f}_{i} - S^{\prime\prime}_{\ns} {k_r}_{i}\right)&\dconv
 \end{align}
\end{subequations}

\subsection{Pressure modification\slash Falloff function derivatives}

>>>>

\documentclass[12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{csquotes}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage[
    backend=biber,
    style=numeric,
    citestyle=numeric,
    sorting=none
]{biblatex}
\addbibresource{derivations.bib}

% dcases
\usepackage{mathtools}
% for text right arrow
\usepackage{textcomp}
\usepackage{amssymb}
\usepackage{amsmath,eqparbox,xparse}
\usepackage[breaklinks=true, linkcolor=blue, citecolor=blue, colorlinks=true]{hyperref}
% load after hyperref
\usepackage[english,capitalise]{cleveref}

% https://tex.stackexchange.com/a/34412/5764
\makeatletter
\NewDocumentCommand{\eqmathbox}{o O{c} m}{%
  \IfValueTF{#1}
    {\def\eqmathbox@##1##2{\eqmakebox[#1][#2]{$##1##2$}}}
    {\def\eqmathbox@##1##2{\eqmakebox{$##1##2$}}}
  \mathpalette\eqmathbox@{#3}
}
\makeatother

\newcommand{\pluseq}{\mathrel{{+}{=}}}
\newcommand{\minuseq}{\mathrel{{-}{=}}}
\newcommand{\ns}{\ensuremath{{N_{sp}}}}
\newcommand{\nr}{\ensuremath{{N_{reac}}}}
\newcommand{\conp}{CONP}
\newcommand{\conv}{CONV}
\newcommand{\dconp}{\ensuremath{\text{for \conp,}}}
\newcommand{\dconv}{\ensuremath{\text{for \conv,}}}
\newcommand{\Ru}{\ensuremath{\mathcal{R}}}

% treat subequations as equation for cleverref
% https://tex.stackexchange.com/a/308627/56227
\crefalias{subequation}{equation}

@@

\subsection{Reaction rate expressions}
The net species rate of production is defined as:
\begin{equation}
 \label{e:spec_rop}
 \dot{\omega}_{k} = \sum_{i=1}^{\nr} \nu_{k,i} q_{i}
\end{equation}
where $\nr$ is the number of reactions in the chemical kinetic model, $\nu_{k, i}$ the overall stoichiometric coefficient of species $k$ in reaction $i$ and $q_i$ the net rate-of-progress for reaction $i$:
\begin{align}
\nu_{k,i} &= \nu^{\prime\prime}_{k,i} - \nu^{\prime}_{k,i} \\
q_{i} &= R_{i} c_{i}
\end{align}
with $\nu^{\prime}_{k,i}$ and $\nu^{\prime\prime}_{k,i}$ the product and reactant stoichiometric cofficients (respectively) of species $k$ in reaction $i$.
The base rate-of-progress for the $i$th reversible reaction $R_{i}$ is given by:
\begin{align}
R_{i} &= {R_f}_{i} - {R_r}_{i} \label{e:ropnet}\\
{R_f}_{i} &= {k_f}_{i} \prod_{k=1}^{\ns} [C]_{k}^{\nu^{\prime}_{k,i}} \label{e:ropf}\\
{R_r}_{i} &= {k_r}_{i} \prod_{k=1}^{\ns} [C]_{k}^{\nu^{\prime\prime}_{k,i}} \label{e:ropr}
\end{align}
where ${k_f}_{i}$ and ${k_r}_{i}$ are the forward and reverse reaction coefficients (respectively) for the $i$th reaction, and the third-body\slash pressure modification $c_{i}$ is given by:
\begin{equation}
\label{e:rxn_pressure}
c_i = \begin{dcases}
  1 &\text{for elementary reactions,} \\
  [X]_i &\text{for third-body enhanced reactions,} \\
  \frac{P_{r,i}}{1 + P_{r,i}} F_i &\text{for unimolecular\slash~recombination fall-off reactions, and} \\
  \frac{1}{1 + P_{r,i}} F_i &\text{for chemically-activated bimolecular reactions,}
  \end{dcases}
\end{equation}
where for the $i$th reaction $[X]_i$ is the third-body concentration, $P_{r,i}$ is the reduced pressure, and $F_i$ is the falloff blending factor.
These terms are defined in the following sections.

@@

\subsection{Falloff reactions}
Unlike elementary and third-body reactions, falloff reactions exhibit a pressure dependence described as a blending of rates at low- and high-pressure limits; thus, the rate coefficients depend on a mixture of low-pressure- ($k_{0, i}$) and high-pressure-limit ($k_{\infty,i}$) coefficients, each with corresponding Arrhenius parameters and expressed using Eq.~\cref{e:arrhenius}.
The ratio of the coefficients $k_{0, i}$ and $k_{\infty, i}$, combined with the third-body concentration (based on either the mixture as a whole including any efficiencies $\alpha_{k,i}$, or a specific species), define a reduced pressure $P_{r,i}$ given by
\begin{equation}
 \label{e:pr}
 P_{r, i}=\frac{[X]_{i} k_{0, i}}{k_{\infty, i}}
\end{equation}
where $[X]_{i}$ is the appropriate third-body concentration as described in~\cref{s:thdbody}

@@

\subsection{Species rate of production derivatives}
First, we evaluate the derivatives of the net species rate of production equation~\cref{e:spec_rop}, with respect to temperature:
\begin{equation}
 \label{e:dwdot_dT}
 \frac{\partial \dot{\omega} }{\partial T }_{k} = \sum_{i=1}^{\nr} \left(\nu_{k,i} R_{i} \frac{\partial c }{\partial T }_{i} + \nu_{k,i} \frac{\partial R }{\partial T }_{i} c_{i}\right) \;,
\end{equation}
other species:
\begin{equation}
 \label{e:dwdot_dnj}
 \frac{\partial \dot{\omega} }{\partial {n_j} }_{k} = \sum_{i=1}^{\nr} \left(\nu_{k,i} R_{i} \frac{\partial c }{\partial {n_j} }_{i} + \nu_{k,i} \frac{\partial R }{\partial {n_j} }_{i} c_{i}\right)
\end{equation}
and the state parameter:
\begin{subequations}
 \label{e:dwdot_de}
 \begin{align}
  \frac{\partial \dot{\omega} }{\partial V }_{k} &= \sum_{i=1}^{\nr} \left(\nu_{k,i} R_{i} \frac{\partial c }{\partial V }_{i} + \nu_{k,i} \frac{\partial R }{\partial V }_{i} c_{i}\right)\dconp,\\
  \frac{\partial \dot{\omega} }{\partial P }_{k} &= \sum_{i=1}^{\nr} \left(\nu_{k,i} R_{i} \frac{\partial c }{\partial P }_{i} + \nu_{k,i} \frac{\partial R }{\partial P }_{i} c_{i}\right)\dconv
 \end{align}
\end{subequations}

@@

Finally, combining~\cref{e:dropf_dt,e:dropr_dt} gives the total temperature derivative of the net rate of progress:
\begin{align}
 \label{e:drop_dt}
 \frac{\partial R }{\partial T }_{i} =& \frac{{R_f}_{i}}{T} \left(\beta_{i} + \frac{{E_{a}}_{i}}{T \Ru}\right) - \left(- \sum_{k=1}^{\ns} \nu_{k,i} \frac{\text{d} B }{\text{d} T }_{k} + \frac{1}{T} \left(\beta_{i} + \frac{{E_{a}}_{i}}{T \Ru}\right)\right) {R_r}_{i} \nonumber \\
				      &\qquad + \frac{[C] S^{\prime\prime}_{\ns}}{T} {k_r}_{i} - \frac{[C] S^{\prime}_{\ns}}{T} {k_f}_{i}
\end{align}
\subsubsection{Molar derivative}
\label{s:rop_molar}
The derivative of the forward rate of progress with respect to the amount of moles of a species $j$ is:
\begin{equation}
 \frac{d}{d n_{k}} {R_{f_i}} = \left(\frac{\partial}{\partial n_{j}} \prod_{k=1}^{\ns} [C]_{k}^{\nu^{\prime}_{k,i}}\right) {k_f}_{i} \;.
\end{equation}
The derivative of a species concentration with respect to moles of a species $j$ is given as:
\begin{equation}
 \frac{\partial [C_k]}{\partial n_j} =
 \begin{dcases}
 \frac{\delta_{j k}}{V} & k \ne \ns \\
 -\frac{1}{V} & k = \ns
 \end{dcases}
\end{equation}
Or put succinctly:
\begin{equation}
\label{e:dck_dnj}
\frac{\partial [C_k]}{\partial n_j} = \frac{\delta_{j k} - \delta_{\ns k}}{V} \;.
\end{equation}
Using~\cref{e:dck_dnj} the molar derivative of the forward rate of progress is found as:
\begin{equation}
 \frac{\partial {R_f}_{i} }{\partial {n_j} } = {k_f}_{i} \sum_{k=1}^{\ns} \left(- \frac{\delta_{\ns k}}{V} + \frac{\delta_{j k}}{V}\right) \nu^{\prime}_{k,i} [C]_{k}^{\nu^{\prime}_{k,i} - 1} \prod_{\substack{1 \leq l \leq k - 1\\k + 1 \leq l \leq \ns}} [C]_{l}^{\nu^{\prime}_{l,i}}
\end{equation}
with the same temporary variables $S^{\prime}_{j}$ and $S^{\prime}_{\ns}$ as defined previously, this can be simplified to:
\begin{equation}
 \label{e:dropf_dnj}
 \frac{\partial {R_f}_{i} }{\partial {n_j} } = \frac{{k_f}_{i}}{V} \left(- S^{\prime}_{\ns} + S^{\prime}_{j}\right)
\end{equation}
and by the same process, the reverse rate of progress derivative is found to be:
\begin{equation}
 \label{e:dropr_dnj}
 \frac{\partial {R_r}_{i} }{\partial {n_j} } = \frac{{k_r}_{i}}{V} \left(- S^{\prime\prime}_{\ns} + S^{\prime\prime}_{j}\right)
\end{equation}
and the net rate of progress molar derivative:
\begin{equation}
 \frac{\partial R_{i} }{\partial {n_j} } = - \frac{{k_r}_{i}}{V} \left(- S^{\prime\prime}_{\ns} + S^{\prime\prime}_{j}\right) + \frac{{k_f}_{i}}{V} \left(- S^{\prime}_{\ns} + S^{\prime}_{j}\right)
\end{equation}

@@

Following the outline of~\cref{s:rop_molar}, the forward rate of progress derivatives are:
\begin{subequations}
 \begin{align}
  \frac{\partial {R_f}_{i} }{\partial V } &= \frac{[C] S^{\prime}_{\ns}}{V} {k_f}_{i} - \frac{{R_f}_{i}}{V} \sum_{k=1}^{\ns} \nu^{\prime}_{k,i}&\dconp\\
  \frac{\partial {R_f}_{i} }{\partial P } &= \frac{S^{\prime}_{\ns} {k_f}_{i}}{T \Ru}&\dconv
 \end{align}
\end{subequations}
and similarly, the reverse rate of progress derivatives:
\begin{subequations}
 \begin{align}
  \frac{\partial {R_r}_{i} }{\partial V } &= \frac{[C] S^{\prime\prime}_{\ns}}{V} {k_r}_{i} - \frac{{R_r}_{i}}{V} \sum_{k=1}^{\ns} \nu^{\prime\prime}_{k,i}&\dconp\\
  \frac{\partial {R_r}_{i} }{\partial P } &= \frac{S^{\prime\prime}_{\ns} {k_r}_{i}}{T \Ru}&\dconv
 \end{align}
\end{subequations}
giving finally:
\begin{subequations}
 \label{e:dropi_de}
 % linebreak and parenthesis sizing:
 % https://tex.stackexchange.com/questions/49890/linebreak-between-left-and-right/49895
 \begin{align}
  \frac{\partial {R}_{i} }{\partial V } &= \frac{1}{V}\left(\vphantom{{R_r}_{i} \sum_{k=1}^{\ns} \nu^{\prime\prime}_{k,i}} [C]\left(S^{\prime}_{\ns} {k_f}_{i} - S^{\prime\prime}_{\ns} {k_r}_{i}\right) + \right.& \nonumber\\
  &\left. \quad\left({R_r}_{i} \sum_{k=1}^{\ns} \nu^{\prime\prime}_{k,i} - {R_f}_{i} \sum_{k=1}^{\ns} \nu^{\prime}_{k,i}\right) \right)&\dconp\\
  \frac{\partial {R}_{i} }{\partial P } &= \frac{1}{T \Ru} \left(S^{\prime}_{\ns} {k_f}_{i} - S^{\prime\prime}_{\ns} {k_r}_{i}\right)&\dconv
 \end{align}
\end{subequations}

\subsection{Pressure modification\slash Falloff function derivatives}
\subsubsection{Elementary reactions}
For elementary reactions, all derivatives of the pressure-modification term are zero:
\begin{align}
\eqmathbox[LHS_dci_elem][r]{\frac{\partial c_{i} }{\partial T }} &= 0 & \eqmakebox[cond_dci_elem][r]{,} \label{e:dci_elem_dt} \\
\eqmathbox[LHS_dci_elem][r]{\frac{\partial c_{i} }{\partial {n_j} }} &= 0 & \eqmakebox[cond_dci_elem][r]{,} \label{e:dci_elem_dnj} \\
\end{align}
and:
\begin{subequations}
 \label{e:dci_elem_de}
 \begin{align}
  \eqmathbox[LHS_dci_elem][r]{\frac{\partial c_{i} }{\partial V }} &= 0 & \eqmakebox[cond_dci_elem][r]{\dconp} \\
  \eqmathbox[LHS_dci_elem][r]{\frac{\partial c_{i} }{\partial P }} &= 0 & \eqmakebox[cond_dci_elem][r]{\dconv}
 \end{align}
\end{subequations}

\subsubsection{Third-body enhanced reactions}
For a third-body enhanced reaction~\cref{e:thd_mix} is differentiated to give:
\begin{align}
 \eqmathbox[LHS_dci][r]{\frac{\partial [X]_i }{\partial T }} &= \eqmathbox[RHS_dci][l]{-\frac{[C] \alpha_{\ns,i}}{T}} & \eqmakebox[cond_dci_thd][r]{,} \label{e:dci_thd_dt} \\
 \eqmathbox[LHS_dci][r]{\frac{\partial [X]_i }{\partial n_{j}}} &= \eqmathbox[RHS_dci][l]{\frac{1}{V} \left(- \alpha_{\ns,i} + \alpha_{j,i}\right)} & \eqmakebox[cond_dci_thd][r]{,} \label{e:dci_thd_dnj}
\end{align}
and:
\begin{subequations}
 \label{e:dci_thd_de}
 \begin{align}
  \eqmathbox[LHS_dci][r]{\frac{\partial [X]_i }{\partial V }} &= \eqmathbox[RHS_dci][l]{\frac{1}{V} \left([C] \alpha_{\ns,i} - [X]_{i}\right)} & \eqmakebox[cond_dci_thd][r]{\dconp}\\
  \eqmathbox[LHS_dci][r]{\frac{\partial [X]_i }{\partial P }} &= \eqmathbox[RHS_dci][l]{\frac{\alpha_{\ns,i}}{T \Ru}} & \eqmakebox[cond_dci_thd][r]{\dconv}
 \end{align}
\end{subequations}

If $\alpha_{j,i} = 1$ for all species $j$,~\cref{e:dci_thd_dt,e:dci_thd_dnj,e:dci_thd_de} may be simplified to:
\begin{align}
 \eqmathbox[lhs_dci_thd_unity][r]{\frac{\partial c_{i} }{\partial T }} &= \eqmathbox[rhs_dci_thd_unity][l]{- \frac{[C]}{T}}& \eqmakebox[cond_dci_thd_unity][r]{,} \label{e:dci_thd_unity_dt} \\
 \eqmathbox[lhs_dci_thd_unity][r]{\frac{\partial c_{i} }{\partial n_{j} }} &= \eqmathbox[rhs_dci_thd_unity][l]{0}& \eqmakebox[cond_dci_thd_unity][r]{,}
\end{align}
and:
\begin{subequations}
 \label{e:dci_thd_unity_de}
 \begin{align}
  \eqmathbox[lhs_dci_thd_unity][r]{\frac{\partial c_{i} }{\partial V }} &= \eqmathbox[rhs_dci_thd_unity][l]{0} & \eqmakebox[cond_dci_thd_unity][r]{\dconp} \\
  \eqmathbox[lhs_dci_thd_unity][r]{\frac{\partial c_{i} }{\partial P }} &= \eqmathbox[rhs_dci_thd_unity][l]{\frac{1}{T \Ru}}&\eqmakebox[cond_dci_thd_unity][r]{\dconv}
 \end{align}
\end{subequations}

If the third-body is the $m$th species,~\cref{e:dci_thd_dt,e:dci_thd_dnj,e:dci_thd_de} become:
\begin{align}
 \eqmathbox[lhs_dci_thd_spec][r]{\frac{\partial c_{i} }{\partial T }} &= \eqmathbox[rhs_dci_thd_spec][l]{-\frac{\delta_{\ns m}}{T} [C]}&\eqmakebox[cond_dci_thd_spec][r]{,} \label{e:dci_thd_spec_dt} \\
 \eqmathbox[lhs_dci_thd_spec][r]{\frac{\partial c_{i} }{\partial n_j }} &= \eqmathbox[rhs_dci_thd_spec][l]{\frac{1}{V} \left(- \delta_{\ns m} + \delta_{j m}\right)}&\eqmakebox[cond_dci_thd_spec][r]{,} \label{e:dci_thd_spec_dnj} \\
\end{align}
and:
\begin{subequations}
\label{e:dci_thd_spec_de}
\begin{align}
\eqmathbox[lhs_dci_thd_spec][r]{\frac{\partial c_{i} }{\partial V }} &= \eqmathbox[rhs_dci_thd_spec][l]{\frac{\delta_{\ns m}}{V} \left([C] - [C]_{\ns}\right) + \frac{[C]_{m}}{V} \left(\delta_{\ns m} - 1\right)} & \eqmakebox[cond_dci_thd_spec][r]{\dconp} \\
\eqmathbox[lhs_dci_thd_spec][r]{\frac{\partial c_{i} }{\partial P }} &= \eqmathbox[rhs_dci_thd_spec][l]{\frac{\delta_{\ns m}}{T \Ru}} & \eqmakebox[cond_dci_thd_spec][r]{\dconv}
\end{align}
\end{subequations}

\subsubsection{Unimolecular\slash~recombination fall-off reactions}
\label{s:dfall}
Derivatives of the third-body pressure modification term for unimolecular\slash~recombination fall-off reactions---given by~\cref{e:rxn_pressure}---are quite involved, and will be broken up over the next sections.
The derivative of full third-body pressure modification term for fall-off reactions will be given in this section, while~\cref{s:dchem} will provide the same derivatives for chemically-activated bimolecular reactions.
Subsequently, the derivatives of the reduced pressure and falloff blending factors will be explored in~\cref{s:dpr,s:dfi} respectively.

The derivatives of the unimolecular\slash~recombination fall-off reaction third-body pressure modification term are:
\begin{align}
 \eqmathbox[lhs_dci_fall][r]{\frac{\partial c_{i} }{\partial T }} &= \eqmathbox[rhs_dci_fall][l]{\frac{1}{P_{r, i} + 1} \left(P_{r, i} \frac{\partial F_{i} }{\partial T } + \frac{\partial P_{r, i} }{\partial T } \left(F_{i} - c_{i}\right)\right)} & \eqmakebox[cond_dci_fall][r]{,} \label{e:dci_fall_dt}\\
 \eqmathbox[lhs_dci_fall][r]{\frac{\partial c_{i} }{\partial n_j}} &= \eqmathbox[rhs_dci_fall][l]{\frac{1}{P_{r, i} + 1} \left(P_{r, i} \frac{\partial F_{i} }{\partial n[j] } + \frac{\partial P_{r, i} }{\partial n_j } \left(F_{i} - c_{i}\right)\right)} & \eqmakebox[cond_dci_fall][r]{,} \label{e:dci_fall_dnj}
\end{align}
and with respect to the thermodynamic parameter:
\begin{subequations}
 \label{e:dci_fall_de}
 \begin{align}
  \eqmathbox[lhs_dci_fall][r]{\frac{\partial c_i }{\partial V }} &= \eqmathbox[rhs_dci_fall][l]{\frac{1}{P_{r, i} + 1} \left(P_{r, i} \frac{\partial F_{i} }{\partial V } + \frac{\partial P_{r, i} }{\partial V } \left(F_{i} - c_{i}\right)\right)} & \eqmakebox[cond_dci_fall][r]{\dconp} \\
  \eqmathbox[lhs_dci_fall][r]{\frac{\partial c_i }{\partial P }} &= \eqmathbox[rhs_dci_fall][l]{\frac{1}{P_{r, i} + 1} \left(P_{r, i} \frac{\partial F_{i} }{\partial P } + \frac{\partial P_{r, i} }{\partial P } \left(F_{i} - c_{i}\right)\right)} & \eqmakebox[cond_dci_fall][r]{\dconv}
 \end{align}
\end{subequations}

\subsubsection{Chemically-activated bimolecular reactions}
\label{s:dchem}

Similarly, the chemically-activated bimolecular reactions are as follows:
\begin{align}
 \label{e:dci_chem_dt}
 \eqmathbox[lhs_dci_chem][r]{\frac{\partial c_i }{\partial T }} &= \eqmathbox[rhs_dci_chem][l]{\frac{1}{P_{r, i} + 1} \left(\frac{\partial F_{i} }{\partial T } - \frac{\partial P_{r, i} }{\partial T } c_{i}\right)} & \eqmakebox[cond_dci_chem][r]{,} \\
 \label{e:dci_chem_dnj}
 \eqmathbox[lhs_dci_chem][r]{\frac{\partial c_i }{\partial n_j }} &= \eqmathbox[rhs_dci_chem][l]{\frac{1}{P_{r, i} + 1} \left(\frac{\partial F_{i} }{\partial n_j } - \frac{\partial P_{r, i} }{\partial n_j } c_{i}\right)} & \eqmakebox[cond_dci_chem][r]{,}
\end{align}
and:
\begin{subequations}
 \label{e:dci_chem_de}
 \begin{align}
  \eqmathbox[lhs_dci_chem][r]{\frac{\partial c_i }{\partial V }} &= \eqmathbox[rhs_dci_chem][l]{\frac{1}{P_{r, i} + 1} \left(\frac{\partial F_{i} }{\partial V } - \frac{\partial P_{r, i} }{\partial V } c_{i}\right)} & \eqmakebox[cond_dci_chem][r]{\dconp} \\
  \eqmathbox[lhs_dci_chem][r]{\frac{\partial c_i }{\partial P }} &= \eqmathbox[rhs_dci_chem][l]{\frac{1}{P_{r, i} + 1} \left(\frac{\partial F_{i} }{\partial P } - \frac{\partial P_{r, i} }{\partial P } c_{i}\right)} & \eqmakebox[cond_dci_chem][r]{\dconv}
 \end{align}
\end{subequations}

\subsubsection{Reduced pressure}
\label{s:dpr}
